---
title: "Profiling of clusters"
output: pdf_document
date: "2022-12-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
library(FactoMineR)
```


```{r}
df <- readRDS("hcluster.rds")

# Rename vars with ? because it causes problems
names(df) <- gsub("(.*)\\?", "\\1", names(df))

dim(df)
names(df)

cluster_vars <- c(5, 6, 2, 20, 43:51, 34:42)
names(df[,cluster_vars])
```


## Graphical profiling

### Numerical

```{r}
for (v in c("Age", "BodyweightKg")) {
  pl <- ggplot(df, aes_string(x="cluster", y=v, fill="cluster")) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.7) +
    geom_hline(yintercept=mean(df[,v]), linetype="dashed", color = "red", size=1)
  print(pl)
}
```



```{r}
for (cat in c("Squat", "Bench", "Deadlift")) {
  for (att in c("", "Inc1", "Inc2")) {
    v <- paste0(cat, att)
    pl <- ggplot(df, aes_string(x="cluster", y=v, fill="cluster")) +
      geom_boxplot() +
      geom_jitter(color="black", size=0.4, alpha=0.7) +
      geom_hline(yintercept=mean(df[,v]), linetype="dashed", color = "red", size=1)
    print(pl)
  }
}
```


### Categorical

```{r}
# Total counts
ggplot(df, aes(x=cluster, y=stat(count))) +
  geom_bar()
```


```{r}
for (v in c("Sex", "Country")) {
  pl <- ggplot(df, aes_string(x="cluster", fill=v)) +
    geom_bar(position="fill") +
    labs(y = "Proportion")
  print(pl)
}
```

```{r}
for (cat in c("Squat", "Bench", "Deadlift")) {
  for (att in c("1", "2", "3")) {
    v <- paste0("Lifted", cat, att, "Kg")
    pl <- ggplot(df, aes_string(x="cluster", fill=v)) +
      geom_bar(position="fill") +
      labs(y = "Proportion")
    print(pl)
  }
}
```

## Statistical profiling

```{r}
dfcl <- df[,c(cluster_vars, 55)]
names(dfcl)
catdes(dfcl, 23, proba = 0.01)
```

## Selected relevant variables

* Cluster 1
	* Qualitative
		* More male: 85.5% of this cluster is male (global 63.0%)
        * More successful lift attempts
            * Squat 1, 2
        * More failed attempts
            * Squat 3
            * Deadlift 1, 2, 3 
            * Bench 1, 2
		* Less people from England
	* Quantitative
		* More first tried weight in deadlift, squat and bench
		* A little more body weight (84 vs 81)
		* Younger (27 vs 29)
* Cluster 2
	* Qualitative
		* More female: 99.7% of this cluster is female (global 37.0%) 64.4 female are on this cluster.
		* More successful lift attempts
			* Squat 1, 2
			* Bench 1
			* Deadlift 1, 2, 3
        * More England less Germany
	* Quantitative
		* Older (30.0 vs 28.8)
        * Less body weight (68.4 vs 80.7)
        * Less starting weight
            * Squat
            * Bench
            * Deadlift (58.2 vs 96.8)
        * Less weight increments
            * Squat 1, 2
            * Bench 1, 2
            * Deadlift 1, 2
* Cluster 3
	* Qualitative
        * More successful attempts
            * Squat 1
            * Deadlift 1
        * More failed attempts
            * Squat 2, 3
            * Bench 2, 3
            * Deadlift 3
	* Quantitative
        * More increment in Squat 1
        * Less increment in Squat 2
* Cluster 4
	* Qualitative
        * More male: 100.0% of this cluster is male (global 63.0%)
        * More successful attempts
            * Squat 1, 2, 3
            * Bench 1, 2, 3
            * Deadlift 1, 2, 3
        * More Germany less USA
	* Quantitative
        * More body weight (88.9 vs 80.7)
        * More starting weight
            * Squat (177.2 vs 151.5)
            * Bench (118.9 vs 96.8)
            * Deadlift (203.2 vs 172.5)
        * More weight increments
            * Squat 1, 2
            * Bench 1, 2
            * Deadlift 1, 2
* Cluster 5
	* Qualitative
        * More successful attempts
            * Bench 1
        * More failed attempts
            * Squat 1, 2 (99.2 vs 11.9), (24.4, 17.3)
            * Bench 2, 3
            * Deadlift 3
        * More USA (55.3 vs 49.1)
	* Quantitative
        * Older (30.0 vs 28.8)
        * Less starting weight
            * Deadlift (164.4 vs 172.5)
        * Less weight increment
            * Squat 1
        * More weight increment
            * Squat 2


## Cluster templates

* Cluster 1: Younger mostly male with a little more bodyweight, trying more weight in first attempts and failing on bench and deadlift but succeeding at squat.
* Cluster 2: Older female with less body weight, trying less starting weights and increments and mostly succeeding. More from England and less from Germany.
* Cluster 3: 
* Cluster 4: Male with more bodyweight, more starting weight and increments with successfull attempts. More Germany less USA.
* Cluster 5:
